---
title: "Politics in the Lab: Data Cleanong and Analysis... sort of"
author: "Wyatt King & Oliver Fuisz"
date: "2025-04-20"
output: html_document
---

```{r}
library(readxl)
library(dplyr)
library(webshot2)
library(gt)
library(ggplot2)
library(tidyr)
library(stargazer)
```

# Data Cleaning

```{r}
getwd()
files<- list.files("New folder")
paths<-files[c(1, 5:12, 2:4)]
```

First, we're going to build a data frame that compiles all of the individual spreadsheets into one larger, cumulative spreadsheet.

```{r}
data<- data.frame()
for(i in seq_along(paths)){
  df<- data.frame()
  for(j in 3:23){
    excel<- read_xlsx(paste0("New folder/", paths[i]), sheet=j, range = "B3:G7")
    excel<- excel %>%
      mutate(Game= paste0("Game ", j-2)) # Create a column indicating the game number
    df<- rbind(df, excel)
  }
  df<- df %>%
    mutate(Player= paste0("Player ", i)) # Create a column indicating the player number
  data<- rbind(data, df)
}
```

Next, we're going to merge with the player assignments spreadsheet to get players' initial allocations and whether they were play even or odd splits. We need to reorganize this spreadsheet to be able to merge it with the above.

```{r}
# Call the player assignments
player_assignments<- read.csv("Player Assignment - Static Sheet.csv")

# Drop the trial rounds
player_assignments<-player_assignments[-c(66:71)]
player_assignments<-player_assignments %>%
  mutate(Player..= paste("Player", Player..))
player_assignments<-player_assignments[,-2]
```

We're going to rename columns to make them easier to work with.

```{r}
cols<-colnames(player_assignments)
cols_split<-strsplit(cols, "Round.")
column_vector<- vector(mode="character", length=length(cols))
for(j in seq_along(cols_split)){
  if(grepl(" ", cols_split[j])== TRUE){
    cols_split[[j]]<- paste("Game", cols_split[[j]])[2]
  }
  column_vector[j]<- cols_split[[j]]
}
colnames(player_assignments)<- column_vector
colnames(player_assignments)[1]<- "Player"
```

We split the columns into groups of three containing the game number, whether the split is odd or even, and the initial allocation.

```{r}
split_into_threes<-split(colnames(player_assignments)[-1], ceiling(seq_along(colnames(player_assignments)) / 3))
split_into_threes<-split_into_threes[-length(split_into_threes)]
```

Next, we create a for loop that merges the above groupings of three into one data frame.

```{r}
reorganized_pa<- data.frame()
for(j in seq_along(split_into_threes)){
  get_cols<- c("Player", split_into_threes[[j]])
  filter_df<- player_assignments[get_cols]
  filter_df<- filter_df %>%
    mutate(Game= split_into_threes[[j]][1])
  colnames(filter_df)<- c("Player", "opponent", "split", "i_allocation", "Game")
  reorganized_pa<- rbind(reorganized_pa, filter_df)
}
```

Next, we merge both the game spreadsheets with the player assignment spreadsheet.

```{r}
merged_df<- merge(data, reorganized_pa, by=c("Player", "Game"))
merged_df<-merged_df[, c("Player", "Game", "opponent", "Round Number", "Your Play", "Opponent's Play", "Your Current Allocation", "Opponent's Current Allocation")]
```

It seems as if there is a discrepency between the player assignment spreadsheet and the allocations people were actually playing. Hence, we create a function that gets players actual initial allocation.

```{r}
get_initial<-function(x){
  if(is.na(x)){
    return(NA)
  }
  else if(x> 17 & x < 23){
    return(20)
  }
  else{
    return(11)
  }
}
```

Now, we create a new data frame that includes players' actual initial allocations (to do so, we use the initial allocations from their player spreadsheets).

```{r}
updated_df<-data.frame()
for(j in seq_along(unique(merged_df$Player))){
  player_to_search<- paste("Player", j)
  search_player<- merged_df[merged_df$Player== player_to_search,]
  for(i in seq_along(unique(search_player$Game))){
    game_to_search<- paste("Game", i)
    search_game<- search_player[search_player$Game== game_to_search,]
    search_game<- search_game[order(search_game$`Round Number`, decreasing=F),]
    change_col<- search_game %>%
      mutate(pi_allocation= get_initial(search_game$`Your Current Allocation`[1])) %>%
      mutate(oi_allocation=get_initial(search_game$`Opponent's Current Allocation`[1]))
    updated_df<- rbind(updated_df, change_col)
  }
}
```

Next, we generate a function that categorizes players' games based on if they played an odd or even splitt.

```{r}
# We create a function that characterizes splits in our data
split_c<- function(x, y){
  if(x==y & x==11){
    return("even")
  }
  else if(x != y){
    return("odd")
  }
  else if(x==y & x==20){
    return(NA)
  }
}
updated_df$split<- mapply(split_c, updated_df$pi_allocation, updated_df$oi_allocation)
```

```{r}
df_r1<- na.omit(updated_df[updated_df$`Round Number`==1,])


nrow(df_r1[df_r1$split=="even",])/2
nrow(df_r1[updated_df$split=="odd",])/2
```


We calculate the proportion of games that were even splits and the proportion of games that were odd splits.

```{r}
mean(updated_df$split== "even", na.rm=T)
mean(updated_df$split== "odd", na.rm=T)
```


We write our data locally.

```{r}
write_path<- paste0("Uncleaned Data.csv")
write.csv(updated_df, file=write_path)
```

We clean our data to exclude circumstances where there is a 20-20 split. We lose a minimal amount of data from doing this (around 1.5% of the total).

```{r}
cleaned_df<-updated_df[is.na(updated_df$split)==F,]

# Amount of data we lost from cleaning
1-nrow(cleaned_df)/nrow(updated_df)
```

We write our cleaned data set locally.

```{r}
write_path<- paste0("Cleaned Data.csv")
write.csv(cleaned_df, file=write_path)
```

# Data "Analysis"

### Regression Model

We run a logistic regression to see what factors influence whether players play A or B. A is the positive case.

```{r}
reg_data<-na.omit(cleaned_df)
reg_data$Game<-as.numeric(gsub("[A-Za-z ]", "", reg_data$Game))

colnames(reg_data)<- c("Player", "Game", "opponent", "Round", "y_play", "o_play", "y_c_all", "o_c_all", "pi_allocation", "oi_allocation", "split")

convert_y_var<- function(x){
  if(x=="A"){
    return(1)
  }
  else if(x=="B"){
    return(0)
  }
}

reg_data$y_play<- sapply(reg_data$y_play, convert_y_var)
reg_data$split<- as.factor(reg_data$split)
reg_data$Player<- as.factor(reg_data$Player)
```

```{r}
m1<-glm(y_play~Round+Game+pi_allocation+oi_allocation+Player, family="binomial", data=reg_data)
sum_m1<-summary(m1)
```

```{r}
reg_df<-as.data.frame(sum_m1$coefficients)
reg_df<-round(reg_df, 3)
```

```{r}
reg_df<- reg_df[-c(6:16),]
```

```{r}
rownames(reg_df)<- c("Constant", "Round", "Game", "Principal Initial Allocation", "Opponenet Initial Allocation")
reg_df<-reg_df[c(2:5, 1), -3]
colnames(reg_df)<- c("Estimate", "Standard Error", "p-value")
```

```{r}
gt::gt(reg_df, rownames_to_stub=T) |>
  tab_header(title="Figure 4", subtitle="Results from Logistic Regression Model") |>
  cols_align("left") |>
  opt_table_font(font=list(google_font(name="Times New Roman"))) |>
  tab_footnote("Note: Fixed effects for players not shown. Estimates represent change in log odds ratio.")
```

### Even: Difference of Proprtions Test

```{r}
diff_prop_even<-reg_data[reg_data$split== "even",]
```

```{r}
diff_prop_data<-diff_prop_even %>%
  group_by(Round)%>%
  summarize(n=n(), a=mean(y_play==1)*n())
```

First, we run difference of proportions tests, comparing how respondents play to if they were just randomly selecting either A or B.

```{r}
binom_1<-binom.test(diff_prop_data$a[1], diff_prop_data$n[1])
binom_2<-binom.test(diff_prop_data$a[2], diff_prop_data$n[2])
binom_3<-binom.test(diff_prop_data$a[3], diff_prop_data$n[3])
binom_4<-binom.test(diff_prop_data$a[4], diff_prop_data$n[4])
```

```{r}
binom_tests1<-data.frame(
  "Estimate"= round(c(binom_1$estimate, binom_2$estimate, binom_3$estimate, binom_4$estimate), 3),
  "P-Value"= c(binom_1$p.value, binom_2$p.value, binom_3$p.value, binom_4$p.value),
  row.names = c("Round 1", "Round 2", "Round 3", "Round 4")
)
```


Next, we do the same thing, looking at how they compare to the mixed strategy equilibrium.

```{r}
even_equil<- data.frame(
  Round= c(1, 2, 3, 4),
  eqil= c(1-12/31, 1-7/19, 1-1/3, 1)
)
```

```{r}
binom_5<-binom.test(diff_prop_data$a[1], diff_prop_data$n[1], p=even_equil$eqil[1])
binom_6<-binom.test(diff_prop_data$a[2], diff_prop_data$n[2], p=even_equil$eqil[2])
binom_7<-binom.test(diff_prop_data$a[3], diff_prop_data$n[3], p=even_equil$eqil[3])
binom_8<-binom.test(diff_prop_data$a[4], diff_prop_data$n[4], p=even_equil$eqil[4])
```

```{r}
binom_tests2<-data.frame(
  "Estimate"= round(c(binom_5$estimate, binom_6$estimate, binom_7$estimate, binom_8$estimate), 3),
  "P-Value"= c(binom_5$p.value, binom_6$p.value, binom_7$p.value, binom_8$p.value),
  row.names = c("Round 1", "Round 2", "Round 3", "Round 4")
)
```

```{r}
binom_tests<-merge(binom_tests1, binom_tests2, by="Estimate")
row.names(binom_tests)<-row.names(binom_tests2)
colnames(binom_tests)<- c("Estimate","Random", "Equilibrium")

stargazer(binom_tests, rownames = T, colnames = T, summary=F, title = "Even Split, Binomial Tests")
?stargazer
```


### We conduct another regression looking at the even data

```{r}
even_equil<- data.frame(
  Round= c(1, 2, 3, 4),
  eqil= c(1-12/31, 1-7/19, 1-1/3, 1)
)
```


```{r}
reg_data_even<- reg_data[reg_data$split=="even",]
reg_data_even<- merge(reg_data_even, even_equil, by="Round")

plot(reg_data_even$Round, reg_data_even$eqil)
```

```{r}
reg_m3<- glm(y_play~eqil, data=reg_data_even, family="binomial")
reg_m2<- glm(y_play~eqil+as.factor(Round), data=reg_data_even, family="binomial")
sum_reg_m2<-summary(reg_m2)

coefs_reg2<-sum_reg_m2$coefficients
exp(coefs_reg2)
rownames(coefs_reg2)<- c("Constant", "Eqilibrium", "Round 2", "Round 3")

stargazer(reg_m3, reg_m2, summary = FALSE, rownames = T, title = "")

al_output<-alias(reg_m2)
summary(as.factor(reg_data_even$Round))
```

```{r}
logistf_m2<- logistf(y_play~eqil+as.factor(Round), data=reg_data_even)
```


### Proportion of people who defect in the even split

We generate a table displaying what proportion of people defect in an even split scenario based on the round number.

```{r}
even<- updated_df[updated_df$split=="even",]
no_na_even<- na.omit(even)

categorize_play<-function(x){
  if(x=="A"){
    return(1)
  }
  else if(x=="B"){
    return(0)
  }
}

no_na_even$play_sorted<- sapply(no_na_even$`Your Play`, categorize_play)

even_plays_by_round<-no_na_even %>%
  group_by(`Round Number`) %>%
  summarize("Proportion Defect"= mean(play_sorted), "n"=n())

even_plays_by_round$`Proportion Defect`<- round(even_plays_by_round$`Proportion Defect`, digits=3)

even_plays_by_round$Equilibrium<- c(round(1-12/31, 3), 0.632, 0.667, 1)

even_plays_by_round<-even_plays_by_round[, c("Round Number", "Proportion Defect", "Equilibrium", "n")]
```

```{r}
stargazer(even_plays_by_round, summary = FALSE, rownames = FALSE, title = "Even Split, Play by Round")
```

```{r}
fig_1<-gt(even_plays_by_round) |>
  tab_header(title="Figure 1", subtitle="Play by Round: Even Split") |>
  cols_align("left") |>
  opt_table_font(font=list(google_font(name="Times New Roman")))
print(fig_1)
```

### Proportion of people who defect in the odd split

We generate tables displaying what proportion of people defect in an odd split scenario based on the round number and whether they were the \$20 or \$11 share.

```{r}
odd<- updated_df[updated_df$split=="odd",]
no_na_odd<- na.omit(odd)
no_na_odd$play_sorted<- sapply(no_na_odd$`Your Play`, categorize_play)

all_20<- no_na_odd[no_na_odd$pi_allocation== 20,]
all_11<- no_na_odd[no_na_odd$pi_allocation== 11,]

all_20_plays_by_round<-all_20 %>%
  group_by(`Round Number`) %>%
  summarize("Proportion Defect"= mean(play_sorted), "n"=n())

all_11_plays_by_round<-all_11 %>%
  group_by(`Round Number`) %>%
  summarize("Proportion Defect"= mean(play_sorted), "n"=n())

all_20_plays_by_round$`Proportion Defect`<- round(all_20_plays_by_round$`Proportion Defect`, digits=3)
all_11_plays_by_round$`Proportion Defect`<- round(all_11_plays_by_round$`Proportion Defect`, digits=3)

all_20_plays_by_round$Equilibrium<- c(1, 1, 1, 1)
all_11_plays_by_round$Equilibrium<- c(0, 0, 0, 1)

all_20_plays_by_round<-all_20_plays_by_round[, c("Round Number", "Proportion Defect", "Equilibrium", "n")]
all_11_plays_by_round<-all_11_plays_by_round[, c("Round Number", "Proportion Defect", "Equilibrium", "n")]
```

```{r}
fig_2<-gt::gt(all_20_plays_by_round) |>
  tab_header(title="Figure 2", subtitle="Play by Round: Odd Split, $20") |>
  cols_align("left") |>
  opt_table_font(font=list(google_font(name="Times New Roman")))
print(fig_2)

fig_3<-gt::gt(all_11_plays_by_round) |>
  tab_header(title="Figure 3", subtitle="Play by Round: Odd Split, $11") |>
  cols_align("left") |>
  opt_table_font(font=list(google_font(name="Times New Roman")))
print(fig_3)
```

### Earnings per Game, based on split

We create a for loop that collapses our data such that one row corresponds to one game for one player. We do so because we later want to generate graphs that show players' earnings per game based on their split and the proportion of time that they played either A or B.

```{r}
game_results_df<-data.frame()
for(j in seq_along(unique(cleaned_df$Player))){
  player_to_search<- paste("Player", j)
  search_player<- cleaned_df[cleaned_df$Player== player_to_search,]
  for(i in seq_along(unique(search_player$Game))){
    game_to_search<- paste("Game", i)
    search_game<- search_player[search_player$Game== game_to_search,]
    if(nrow(search_game)==0){
      next
    }
    total_game<- search_game$`Your Current Allocation`
    
    remove_nas<- total_game[is.na(total_game)==F]
    last_val<- remove_nas[length(remove_nas)]
    
    plays<- search_game$`Your Play`
    total_rounds<-length(na.omit(plays))
    number_a<- sum(plays=="A", na.rm=T)
    number_b<- sum(plays=="B", na.rm=T)
    
    game_df<- data.frame("Player ID"=j, "Game"=i, "Split"=unique(search_game$split), "pi_allocation"= unique(search_game$pi_allocation),  "Earned"=last_val, "NumbR"=total_rounds, "NumbA"=number_a, "NumbB"=number_b)
    game_results_df<- rbind(game_results_df, game_df)
  }
}
```

### Overrall Split

First, we create an overall table that shows players' earnings per game irregardless of their initial allocation and whether their split was odd or even.

```{r}
overall_results<- game_results_df %>%
  group_by(Player.ID) %>%
  summarize("EpG"= sum(Earned)/n(), "NumbA"=sum(NumbA), "NumbR"=sum(NumbR),
            "NumbB"=sum(NumbB))

overall_results<- overall_results[-4]

per_player_earnings<- overall_results %>%
  arrange(desc(EpG)) %>%
  mutate(Player.ID = factor(Player.ID, levels = Player.ID))

df_long_overall <- per_player_earnings %>%
  pivot_longer(cols = starts_with("Numb"), names_to = "Category", values_to = "Count")

# Compute proportions
df_long_overall <- df_long_overall %>%
  group_by(Player.ID) %>%
  mutate(Prop = Count / sum(Count)) %>%
  ungroup()

# Multiply proportion by Earnings to get the segment height
rename_cat<-function(x){
  if(x=="NumbA"){
    return("Proportion A")
  }
  else{
    return("Proportion B")
  }
}

df_long_overall <- df_long_overall %>%
  mutate(SegmentHeight = Prop * EpG)

df_long_overall$Category<- sapply(df_long_overall$Category, rename_cat)
```

```{r}
ggplot(df_long_overall, aes(x = Player.ID, y = SegmentHeight, fill = Category)) +
  geom_bar(stat = "identity") +
  labs(x = "Player ID", y = "Earnings per Game", title = "Earnings Per Game", subtitle = "Overrall Performance")+
  theme(
    plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust = 0.5), panel.background = element_rect(fill="white"),
    panel.grid.major.y = element_line(color="grey", size=0.4),
    panel.grid.major.x=element_blank())+
  scale_fill_manual(values=c("Proportion A"= "lightblue4", "Proportion B"="lightblue"))
ggsave("/Users/wyatttheking/Desktop/Spring 2025/Politics in the Lab/Results Photos/Earnings_per_Game_overall.png")
```

### Game Results Even Split

Next, we create a bar chart showing players earnings per game in the even split.

```{r}
game_results_even<- na.omit(game_results_df[game_results_df$Split== "even",])
game_results_odd<- na.omit(game_results_df[game_results_df$Split== "odd",])

per_player_earnings_even<-game_results_even %>%
  group_by(Player.ID) %>%
  summarize("EpG"= sum(Earned)/n(), "NumbA"=sum(NumbA), "NumbR"=sum(NumbR),
            "NumbB"=sum(NumbB))
```

```{r}
per_player_earnings_even<- per_player_earnings_even[-4]

per_player_earnings_even<- per_player_earnings_even %>%
  arrange(desc(EpG)) %>%
  mutate(Player.ID = factor(Player.ID, levels = Player.ID))

df_long <- per_player_earnings_even %>%
  pivot_longer(cols = starts_with("Numb"), names_to = "Category", values_to = "Count")

# Compute proportions
df_long <- df_long %>%
  group_by(Player.ID) %>%
  mutate(Prop = Count / sum(Count)) %>%
  ungroup()

df_long <- df_long %>%
  mutate(SegmentHeight = Prop * EpG)

df_long$Category<- sapply(df_long$Category, rename_cat)

ggplot(df_long, aes(x = factor(Player.ID), y = SegmentHeight, fill = Category)) +
  geom_bar(stat = "identity") +
  labs(x = "Player ID", y = "Earnings per Game", title = "Earnings Per Game", subtitle = "Even Split") +
  theme(
    plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust = 0.5), panel.background = element_rect(fill="white"),
    panel.grid.major.y = element_line(color="grey", size=0.4),
    panel.grid.major.x=element_blank())+
  scale_fill_manual(values=c("Proportion A"= "lightblue4", "Proportion B"="lightblue"))
ggsave("/Users/wyatttheking/Desktop/Spring 2025/Politics in the Lab/Results Photos/Earnings_per_Game_even.png")
```

### Bar Chart for Odd Split, $20 Initial Allocation

```{r}
game_results_odd_20<- na.omit(game_results_df[game_results_df$Split== "odd" & game_results_df$pi_allocation==20,])

per_player_earnings_odd_20<-game_results_odd_20 %>%
  group_by(Player.ID) %>%
  summarize("EpG"= sum(Earned)/n(), "NumbA"=sum(NumbA), "NumbR"=sum(NumbR),
            "NumbB"=sum(NumbB))
```

```{r}
per_player_earnings_odd_20<- per_player_earnings_odd_20[-4]

per_player_earnings_odd_20<- per_player_earnings_odd_20 %>%
  arrange(desc(EpG)) %>%
  mutate(Player.ID = factor(Player.ID, levels = Player.ID))

df_long_odd_20 <- per_player_earnings_odd_20 %>%
  pivot_longer(cols = starts_with("Numb"), names_to = "Category", values_to = "Count")

# Compute proportions
df_long_odd_20 <- df_long_odd_20 %>%
  group_by(Player.ID) %>%
  mutate(Prop = Count / sum(Count)) %>%
  ungroup()

df_long_odd_20 <- df_long_odd_20 %>%
  mutate(SegmentHeight = Prop * EpG)

df_long_odd_20$Category<- sapply(df_long_odd_20$Category, rename_cat)
```

```{r}
ggplot(df_long_odd_20, aes(x = factor(Player.ID), y = SegmentHeight, fill = Category)) +
  geom_bar(stat = "identity") +
  labs(x = "Player ID", y = "Earnings per Game", title = "Earnings Per Game", subtitle = "Odd Split, $20") +
  theme(
    plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust = 0.5), panel.background = element_rect(fill="white"),
    panel.grid.major.y = element_line(color="grey", size=0.4),
    panel.grid.major.x=element_blank())+
  scale_fill_manual(values=c("Proportion A"= "lightblue4", "Proportion B"="lightblue"))

ggsave("/Users/wyatttheking/Desktop/Spring 2025/Politics in the Lab/Results Photos/Earnings_per_game_20.png")
```

### Bar Chart for Odd Split, $11 allocation

```{r}
game_results_odd_11<- na.omit(game_results_df[game_results_df$Split== "odd" & game_results_df$pi_allocation==11,])

per_player_earnings_odd_11<-game_results_odd_11 %>%
  group_by(Player.ID) %>%
  summarize("EpG"= sum(Earned)/n(), "NumbA"=sum(NumbA), "NumbR"=sum(NumbR),
            "NumbB"=sum(NumbB))
```

```{r}
per_player_earnings_odd_11<- per_player_earnings_odd_11[-4]

per_player_earnings_odd_11<- per_player_earnings_odd_11 %>%
  arrange(desc(EpG)) %>%
  mutate(Player.ID = factor(Player.ID, levels = Player.ID))

df_long_odd_11 <- per_player_earnings_odd_11 %>%
  pivot_longer(cols = starts_with("Numb"), names_to = "Category", values_to = "Count")

# Compute proportions
df_long_odd_11 <- df_long_odd_11 %>%
  group_by(Player.ID) %>%
  mutate(Prop = Count / sum(Count)) %>%
  ungroup()

df_long_odd_11 <- df_long_odd_11 %>%
  mutate(SegmentHeight = Prop * EpG)

df_long_odd_11$Category<- sapply(df_long_odd_11$Category, rename_cat)
```

```{r}
ggplot(df_long_odd_11, aes(x = factor(Player.ID), y = SegmentHeight, fill = Category)) +
  geom_bar(stat = "identity") +
  labs(x = "Player ID", y = "Earnings per Game", title = "Earnings Per Game", subtitle = "Odd Split, $11") +
  theme(
    plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust = 0.5), panel.background = element_rect(fill="white"),
    panel.grid.major.y = element_line(color="grey", size=0.4),
    panel.grid.major.x=element_blank())+
  scale_fill_manual(values=c("Proportion A"= "lightblue4", "Proportion B"="lightblue"))
ggsave("/Users/wyatttheking/Desktop/Spring 2025/Politics in the Lab/Results Photos/Earnings_per_game_11.png")
```

### Wrap bar charts

To better display our data, we decide to create a wrapped bar chart divided by the game split and players' initial allocations.

```{r}
df_long_odd_11
df_long_odd_20

odd_20_combine<- df_long_odd_20 %>%
  mutate(Split= "Odd Split, $20")

odd_11_combine<- df_long_odd_11 %>%
  mutate(Split= "Odd Split, $11")

even_to_combine<-df_long %>%
  mutate(Split= "Even Split")
```

```{r}
combine<- rbind(odd_20_combine, odd_11_combine, even_to_combine)
```

```{r}
combine$Player.ID<- as.character(combine$Player.ID)
combine$Player.ID<- as.numeric(combine$Player.ID)
```


```{r}
ggplot(combine, aes(x = factor(Player.ID), y = SegmentHeight, fill = Category)) +
  geom_bar(stat = "identity") +
  labs(x = "Player ID", y = "Earnings per Game (Experimental Dollars)", title = "Figure 1", subtitle="Players' earnings, by game type") +
  theme(
    plot.title = element_text(hjust = 0, face="bold"), 
    plot.subtitle = element_text(hjust = 0), 
    panel.background = element_rect(fill="white"),
    panel.grid.major.y = element_line(color="grey", size=0.4),
    panel.grid.major.x=element_blank(),
    legend.position = c(.7, 0.25),
    text = element_text(family="Times New Roman", size=16),
    plot.margin= margin(t=25,
                        r=25,
                        b=25,
                        l=25))+
  guides(fill=guide_legend(title="Players' Moves"))+
  scale_fill_manual(values=c("Proportion A"= "lightblue4", "Proportion B"="lightblue"))+
  facet_wrap(~ Split, nrow=2, shrink=F, scales="free")

ggsave("/Users/wyatttheking/Desktop/Spring 2025/Politics in the Lab/Results Photos/Panel Wrap7.png", height=10.5, width=8)
```

```{r}
per_player_earnings_odd<- per_player_earnings_even[-4]

per_player_earnings_even<- per_player_earnings_even %>%
  arrange(desc(EpG)) %>%
  mutate(Player.ID = factor(Player.ID, levels = Player.ID))

df_long <- per_player_earnings_even %>%
  pivot_longer(cols = starts_with("Numb"), names_to = "Category", values_to = "Count")

# Compute proportions
df_long <- df_long %>%
  group_by(Player.ID) %>%
  mutate(Prop = Count / sum(Count)) %>%
  ungroup()

# Multiply proportion by Earnings to get the segment height
rename_cat<-function(x){
  if(x=="NumbA"){
    return("Proportion A")
  }
  else{
    return("Proportion B")
  }
}

df_long <- df_long %>%
  mutate(SegmentHeight = Prop * EpG)

df_long$Category<- sapply(df_long$Category, rename_cat)

ggplot(df_long, aes(x = factor(Player.ID), y = SegmentHeight, fill = Category)) +
  geom_bar(stat = "identity") +
  labs(x = "Player ID", y = "Earnings per Game", title = "Earnings Per Game", subtitle = "Even Split") +
  theme(
    plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust = 0.5), panel.background = element_rect(fill="white"),
    panel.grid.major.y = element_line(color="grey", size=0.4),
    panel.grid.major.x=element_blank())+
  scale_fill_manual(values=c("Proportion A"= "lightblue4", "Proportion B"="lightblue"))

ggsave(filenam="/Users/wyatttheking/Desktop/Spring 2025/Politics in the Lab/Results Photos/Earnings Per Game.png", width = 16, height = 9, dpi = 100)
```



```{r}
per_player_earnings_odd<- per_player_earnings_even[-4]

per_player_earnings_even<- per_player_earnings_even %>%
  arrange(desc(EpG)) %>%
  mutate(Player.ID = factor(Player.ID, levels = Player.ID))

df_long <- per_player_earnings_even %>%
  pivot_longer(cols = starts_with("Numb"), names_to = "Category", values_to = "Count")

# Compute proportions
df_long <- df_long %>%
  group_by(Player.ID) %>%
  mutate(Prop = Count / sum(Count)) %>%
  ungroup()

# Multiply proportion by Earnings to get the segment height
rename_cat<-function(x){
  if(x=="NumbA"){
    return("Proportion A")
  }
  else{
    return("Proportion B")
  }
}

df_long <- df_long %>%
  mutate(SegmentHeight = Prop * EpG)

df_long$Category<- sapply(df_long$Category, rename_cat)

ggplot(df_long, aes(x = factor(Player.ID), y = SegmentHeight, fill = Category)) +
  geom_bar(stat = "identity") +
  labs(x = "Player ID", y = "Earnings per Game", title = "Earnings Per Game", subtitle = "Even Split") +
  theme(
    plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust = 0.5), panel.background = element_rect(fill="white"),
    panel.grid.major.y = element_line(color="grey", size=0.4),
    panel.grid.major.x=element_blank())+
  scale_fill_manual(values=c("Proportion A"= "lightblue4", "Proportion B"="lightblue"))
```

### Splits Over Time

```{r}
test_df<-game_results_df %>%
  group_by(Game) %>%
  summarize(Prop_Even= sum(Split=="even"), Prop_Odd= sum(Split=="odd"))

test_df<-test_df[test_df$Game %in% 1:5,]

sum(test_df$Prop_Even)/(sum(test_df$Prop_Even)+sum(test_df$Prop_Odd))

prop_odd_df<-test_df[, c("Game", "Prop_Odd")] %>%
  mutate(Split="Odd")

prop_even_df<-test_df[, c("Game", "Prop_Even")] %>%
  mutate(Split="Even")

colnames(prop_odd_df)[2]<- "Proportion"
colnames(prop_even_df)[2]<- "Proportion"

prop_df<- rbind(prop_odd_df, prop_even_df)

ggplot(data=prop_df, aes(x=factor(Game), y=Proportion, fill=Split))+
         geom_bar(stat="identity")+
  labs(x = "Game", y = "", title = "Figure 1", subtitle = "Play Over Time")
```


### Plays Over Time

```{r}
even_split_df<- game_results_df[game_results_df$Split== "even",]

sum_even_df<- even_split_df %>%
  group_by(Game) %>%
  summarize("PropA"=sum(NumbA)/sum(NumbR), 
            "PropB"=sum(NumbB)/sum(NumbR), 
            "NumbR"=sum(NumbR),
            "NumbG"=length(unique(Player.ID))/2)
```

```{r}
per_round_earnings<-game_results_df %>%
  group_by(Split) %>%
  summarize("NumbA"=sum(NumbA), "NumbB"= sum(NumbB), "NumbR"=sum(NumbR))

even_split<-na.omit(game_results_df[game_results_df$Split=="even",])
even_split %>%
  group_by(Game) %>%
  summarize("PropA"=sum(NumbA)/sum(NumbR), "PropB"= sum(NumbB)/sum(NumbR), "NumbR"=sum(NumbR))


```

```{r}
sum(per_player_earnings$NumbA)/sum(per_player_earnings$NumbR)
```


